---
title: "SimpleViolins"
author: "Alex Badea"
date: "11/29/2021"
output: pdf_document
toc: true
---

---
# Data sources

We evaluate genotype and sex differences in mouse models of Alzheimer's disease risk, based on APOE alleles: APOE2 is protective, APOE3 is control, and APOE4 represents genetic risk for AD. One allele increases risk by 3 times, and two APOE4 alleles increase risk by 10 times (ref) in relation to APOE3 . We use multiple data sources:

Morris Water Maze - testing spatial navigation memory
Segmentation: regional volumes
Microstructural properties: FA
Tractography Based Connectivity: Degree, and Clustering Coefficient

We read the data and normalize volumes to the whole brain.

```{r setup, include=FALSE, echo=FALSE,warning = FALSE}


knitr::opts_chunk$set(echo=FALSE,warning = FALSE)
library(ggpubr)
library(tidyverse)
library(export)
library(gridExtra)
library(scales)
library(ggplot2)
library(cowplot)
library(gplots)
library(tidyverse)
library(patternplot)
library(lme4)
library(visreg)
library(tidyr)
library(magrittr) 
library(dplyr)
library(ggpubr)
library(lme4)
library(lsmeans)
library(emmeans)
library(multcomp)
library(zoo)
#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, echo = FALSE, fig.height=4, fig.width=16, out.width = "80%")

data <- read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_FA.csv")

data_FA <- read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_FA.csv")

data_VOL <- read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_VOL.csv")

data_DEG<-read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_DEG.csv")

data_CLUS<-read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_CLUS.csv")

outpath='/Users/alex/AlexBadea_MyPapers/DavidDunson/Figures/'

my_comparisons <- list( c("APOE22", "APOE33"), c("APOE22", "APOE44"), c("APOE33", "APOE44") )

#?data_FA$APOE<-as.factor(data_FA$APOE)?

data_FA <- data_FA %>% 
   filter(Genotype != "HN") 
data_FA$APOE=data_FA$Genotype

data_VOL <- data_VOL %>% 
   filter(Genotype != "HN") 

data_VOL[,15:347]=data_VOL[,15:347]/data_VOL[,348]
data_VOL$APOE=data_VOL$Genotype

data_DEG <- data_DEG %>% 
   filter(Genotype != "HN") 
data_DEG$APOE=data_DEG$Genotype

data_CLUS <- data_CLUS %>% 
   filter(Genotype != "HN") 
data_CLUS$APOE=data_CLUS$Genotype


# separating by sex
geno_combined_FA <- data_FA
combo_f_FA <- geno_combined_FA %>% 
  filter(Sex == "female")
combo_m_FA <- geno_combined_FA %>% 
  filter(Sex == "male")

geno_combined_VOL <- data_VOL
combo_f_VOL <- geno_combined_VOL %>% 
  filter(Sex == "female")
combo_m_VOL <- geno_combined_VOL %>% 
  filter(Sex == "male")

geno_combined_DEG <- data_DEG
combo_f_DEG <- geno_combined_DEG %>% 
  filter(Sex == "female")
combo_m_DEG <- geno_combined_DEG %>% 
  filter(Sex == "male")

geno_combined_CLUS <- data_CLUS
combo_f_CLUS <- geno_combined_CLUS %>% 
  filter(Sex == "female")
combo_m_CLUS <- geno_combined_CLUS %>% 
  filter(Sex == "male")

dodge <- position_dodge(width = 1)
```


# Plots for fx

We embed plots for day d8 probe trials:

```{r fx plots, echo=FALSE, warning=FALSE}
plot1VOL<-ggplot(data_VOL, aes(Sex, fx, fill = Sex)) +
  geom_violin(inherit.aes=TRUE,position=dodge, alpha=0.8) +
  facet_grid(. ~ Genotype)  +
  geom_boxplot(color="black", outlier.color="black", width=0.2, alpha=.8, position=dodge) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=2, alpha=0.6, position=dodge)+
  #geom_jitter(size = 0.1, height = 0, width = 0.1, aes(color = Sex)) + 
  labs(title = "VOL")+
  theme_minimal()+
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw()+
  labs(x = "genotype", y = "VOL", title = "VOL ") +
  stat_summary(fun.y=median, geom="point", size=2, color="black") +
  theme(legend.position="bottom")+
  theme_bw() 
 

plot1FA<-ggplot(data_FA, aes(Sex, fx, fill = Sex)) +
  geom_violin(inherit.aes=TRUE,position=dodge, alpha=0.8) +
  facet_grid(. ~ Genotype)  +
  geom_boxplot(color="black", outlier.color="black", width=0.2, alpha=.8, position=dodge) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=2, alpha=0.6, position=dodge)+
  #geom_jitter(size = 0.1, height = 0, width = 0.1, aes(color = Sex)) + 
  labs(title = "FA")+
  theme_minimal()+
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw()+
  labs(x = "genotype", y = "FA", title = "FA ") +
  stat_summary(fun.y=median, geom="point", size=2, color="black") +
  theme(legend.position="bottom")+
  theme_bw() 

plot1DEG<-ggplot(data_DEG, aes(Sex, fx, fill = Sex)) +
  geom_violin(inherit.aes=TRUE,position=dodge, alpha=0.8) +
  facet_grid(. ~ Genotype)  +
  geom_boxplot(color="black", outlier.color="black", width=0.2, alpha=.8, position=dodge) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=2, alpha=0.6, position=dodge)+
  #geom_jitter(size = 0.1, height = 0, width = 0.1, aes(color = Sex)) + 
  labs(title = "DEG")+
  theme_minimal()+
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw()+
  labs(x = "genotype", y = "DEG", title = "DEG ") +
  stat_summary(fun.y=median, geom="point", size=2, color="black") +
  theme(legend.position="bottom")+
  theme_bw()

plot1CLUS<-ggplot(data_CLUS, aes(Sex, fx, fill = Sex)) +
  geom_violin(inherit.aes=TRUE,position=dodge, alpha=0.8) +
  facet_grid(. ~ Genotype)  +
  geom_boxplot(color="black", outlier.color="black", width=0.2, alpha=.8, position=dodge) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=2, alpha=0.6, position=dodge)+
  #geom_jitter(size = 0.1, height = 0, width = 0.1, aes(color = Sex)) + 
  labs(title = "CLUS")+
  theme_minimal()+
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw()+
  labs(x = "genotype", y = "CLUS", title = "CLUS ") +
  stat_summary(fun.y=median, geom="point", size=2, color="black") +
  theme(legend.position="bottom")+
  theme_bw()
 

plot<-ggarrange(plot1VOL, plot1FA, plot1DEG, plot1CLUS, 
         # labels = c("Volume", "FA", "DEG", "CLUS" ),
          ncol = 4, nrow = 1, common.legend = TRUE, legend="bottom")

annotate_figure(plot, top = text_grob("fx", 
               color = "black", face = "bold", size = 14))

ggsave(paste(outpath,'fx_4metrics_shortset.pdf',sep=''), plot = last_plot(), device='pdf', scale=1, width=16, height=4, unit=c("in"), dpi=200)



######with stat-compare

plot_stat_VOL<-ggline(geno_combined_VOL, x = "Genotype", y = "fx",
          color = "Genotype", fill = "Genotype", error.plot='errorbar', add='mean_se', palette = c('blueviolet','chartreuse1','red'), size=1, 
       point.size = 1.5, ylab='fx Volume')+ 
 # stat_compare_means(comparisons = my_comparisons)
stat_compare_means(comparisons = my_comparisons, method="t.test")+
  stat_compare_means(label.y = 0.1)

plot_stat_FA<-ggline(geno_combined_FA, x = "Genotype", y = "fx",
          color = "Genotype", fill = "Genotype", error.plot='errorbar', add='mean_se', palette = c('blueviolet','chartreuse1','red'), size=1, 
       point.size = 1.5, ylab='fx FA')+ 
  #stat_compare_means(comparisons = my_comparisons)
stat_compare_means(comparisons = my_comparisons, method="t.test")+
  stat_compare_means(label.y = 0.1)

plot_stat_DEG<-ggline(geno_combined_DEG, x = "Genotype", y = "fx",
          color = "Genotype", fill = "Genotype", error.plot='errorbar', add='mean_se', palette = c('blueviolet','chartreuse1','red'), size=1, 
       point.size = 1.5, ylab='fx DEG')+ 
  #stat_compare_means(comparisons = my_comparisons)
stat_compare_means(comparisons = my_comparisons, method="t.test")+
  stat_compare_means(label.y = 0.1)

plot_stat_CLUS<-ggline(geno_combined_CLUS, x = "Genotype", y = "fx",
          color = "Genotype", fill = "Genotype", error.plot='errorbar', add='mean_se', palette = c('blueviolet','chartreuse1','red'), size=1, 
       point.size = 1.5, ylab='fx CLUS')+ 
 # stat_compare_means(comparisons = my_comparisons)
stat_compare_means(comparisons = my_comparisons, method="t.test")+
  stat_compare_means(label.y = 0.1)
#stat_compare_means(label.y = 45)


plot<-ggarrange(plot_stat_VOL, plot_stat_FA, plot_stat_DEG, plot_stat_CLUS, 
         # labels = c("Volume", "FA", "DEG", "CLUS" ),
          ncol = 4, nrow = 1, common.legend = TRUE, legend="bottom")

annotate_figure(plot, top = text_grob("fx", 
               color = "black", face = "bold", size = 14))

ggsave(paste(outpath,'fx_4metrics_stat_compare2.pdf',sep=''), plot = last_plot(), device='pdf', scale=1, width=16, height=4, unit=c("in"), dpi=200)



#####with stats_compare

#https://rpubs.com/aaronsc32/regression-confidence-prediction-intervals

#fx_VOL_Probe_d5.lm <- lm(Probe_d5 ~ fx, data = cars)
#summary(fx_VOL_Probe_d5.lm)
```

```{r fx_VOL_stats, echo='FALSE'}


print('fx') 

lm_fx_VOL <- lm(fx ~ Genotype*Sex, geno_combined_VOL)
summary(lm_fx_VOL)
lm_fx_VOL_f <- lm(fx ~ Genotype, combo_f_FA)
#summary(lm_fx_VOL_f)
lm_fx_VOL_m <- lm(fx ~ Genotype, combo_m_FA)
#summary(lm_fx_VOL_f)

#plot significance for group comparisons
#my_comparisons <- list( c("APOE22", "APOE33"), c("APOE22", "APOE44"), c("APOE33", "APOE44") )
pfx_Volume<-ggline(geno_combined_VOL, x = "Genotype", y = "fx",
          color = "Genotype", fill = "Genotype", error.plot='errorbar', add='mean_se', palette = c('blueviolet','chartreuse1','red'), size=1, 
       point.size = 1.5, ylab='Volume')+ 
  stat_compare_means(comparisons = my_comparisons) #+ # Add pairwise comparisons p-value
#  stat_compare_means(label.y = 0.01)     # Add global p-value
#xlab='', ylab='Percent SW Distance', legend='top', facet.by='Sex')

#omnibus testing
#https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html#adjust

#33333
sink(paste(outpath, "fx_VOL_SimpleModels.txt"))
mydata.lm <- lm(fx ~ Genotype*Sex, data = geno_combined_VOL)
anova(mydata.lm)
summary(glht(mydata.lm, emm(pairwise ~ Genotype|Sex, adjust="sidak"))) #consider save to file
summary(glht(mydata.lm, emm(pairwise ~ Sex| Genotype)))
sink()
#3333

sink(paste(outpath, "fx_VOL_SimpleStats.txt",sep=''))
'omnibus testing'
joint_tests(ref_grid(lm_fx_VOL)) 
joint_tests(ref_grid(lm_fx_VOL), by = "Sex", adjust = "sidak") 
joint_tests(ref_grid(lm_fx_VOL), by = "Genotype",adjust = "sidak" ) 

'anova'
anova(lm_fx_VOL)
#anova(lm_fx_VOL_f)
#anova(lm_fx_VOL_m)

#post hoc comparison
fx_VOL.emm <- emmeans(lm_fx_VOL , ~ Genotype | Sex, adjust = "sidak")
contrast(fx_VOL.emm, simple = c("Genotype", "Sex")) #FDR
contrast(fx_VOL.emm, simple = list("Genotype", "Sex"))

#post hoc tests
summary(glht(lm_fx_VOL, emm(pairwise ~ Genotype*Sex, contr="sidak"))) #consider save to file
res<-summary(glht(lm_fx_VOL, emm(pairwise ~ Genotype*Sex))) #consider save to file
#summary(as.glht(pairs(lm_fx_VOL.emm), by = NULL))
summary(glht(lm_fx_VOL, emm(pairwise ~ Genotype, contr="sidak")))
summary(glht(lm_fx_VOL, emm(pairwise ~ Genotype | Sex)))
summary(glht(lm_fx_VOL, emm(pairwise ~ Sex | Genotype)))

mypairs<-pairs(fx_VOL.emm) #_consider save to file
pairs(fx_VOL.emm, by="Genotype")
pairs(fx_VOL.emm, by="Sex")


print('fx VOL')
emmip(lm_fx_VOL, ~ Genotype)
emmip(lm_fx_VOL, ~ Genotype | Sex )
emmip(lm_fx_VOL, ~ Sex | Genotype )
emmip(lm_fx_VOL, Genotype~ Sex  )

sink()



plot(fx_VOL.emm, by = NULL, comparisons = TRUE, adjust = "mvt",
horizontal = FALSE, colors = "darkgreen", main ="fx VOL")
ggsave(paste(outpath,'fx_VOL_emmeans.pdf',sep=''), plot = last_plot(), device='pdf', scale=1, width=16, height=4, unit=c("in"), dpi=200)

```

```{r fx_FA_stats, echo='FALSE'}
'simple stats'

print('fx') 

lm_fx_FA <- lm(fx ~ Genotype*Sex, geno_combined_FA)
summary(lm_fx_FA)
lm_fx_FA_f <- lm(fx ~ Genotype, combo_f_FA)
#summary(lm_fx_FA_f)
lm_fx_FA_m <- lm(fx ~ Genotype, combo_m_FA)
#summary(lm_fx_FA_f)


#33333
sink(paste(outpath, "fx_FA_SimpleModels.txt"))
mydata.lm <- lm(fx ~ Genotype*Sex, data = geno_combined_FA)
anova(mydata.lm)
summary(glht(mydata.lm, emm(pairwise ~ Genotype|Sex, adjust="sidak"))) #consider save to file
summary(glht(mydata.lm, emm(pairwise ~ Sex| Genotype)))
sink()
#3333

#omnibus testing
#https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html#adjust

sink(paste(outpath, "fx_FA_SimpleStats.txt",sep=''))
'omnibus testing'
joint_tests(ref_grid(lm_fx_FA)) 
joint_tests(ref_grid(lm_fx_FA), by = "Sex", adjust = "sidak") 
joint_tests(ref_grid(lm_fx_FA), by = "Genotype",adjust = "sidak" ) 

'anova'
anova(lm_fx_FA)
#anova(lm_fx_FA_f)
#anova(lm_fx_FA_m)

#post hoc comparison
fx_FA.emm <- emmeans(lm_fx_FA , ~ Genotype | Sex, adjust = "sidak")
contrast(fx_FA.emm, simple = c("Genotype", "Sex")) #FDR
contrast(fx_FA.emm, simple = list("Genotype", "Sex"))

#post hoc tests
#post hoc tests
summary(glht(lm_fx_FA, emm(pairwise ~ Genotype, contr="sidak")))

summary(glht(lm_fx_FA, emm(pairwise ~ Genotype*Sex, contr="sidak"))) #consider save to file
res<-summary(glht(lm_fx_FA, emm(pairwise ~ Genotype*Sex))) #consider save to file
#summary(as.glht(pairs(lm_fx_FA.emm), by = NULL))
 
summary(glht(lm_fx_FA, emm(pairwise ~ Genotype | Sex)))
summary(glht(lm_fx_FA, emm(pairwise ~ Sex | Genotype)))

mypairs<-pairs(fx_FA.emm) #_consider save to file
pairs(fx_FA.emm, by="Genotype")
pairs(fx_FA.emm, by="Sex")

print('fx FA')
emmip(lm_fx_FA, ~ Genotype)
emmip(lm_fx_FA, ~ Genotype | Sex )
emmip(lm_fx_FA, ~ Sex | Genotype )
emmip(lm_fx_FA, Genotype~ Sex  )
sink()

plot(fx_FA.emm, by = NULL, comparisons = TRUE, adjust = "mvt",
horizontal = FALSE, colors = "darkgreen", main ="fx FA")
ggsave(paste(outpath,'fx_FA_emmeans.pdf',sep=''), plot = last_plot(), device='pdf', scale=1, width=16, height=4, unit=c("in"), dpi=200)

```

```{r fx_DEG_stats, echo='FALSE'}
'simple stats'

print('fx') 

lm_fx_DEG <- lm(fx ~ Genotype*Sex, geno_combined_DEG)
summary(lm_fx_DEG)
lm_fx_DEG_f <- lm(fx ~ Genotype, combo_f_FA)
#summary(lm_fx_DEG_f)
lm_fx_DEG_m <- lm(fx ~ Genotype, combo_m_FA)
#summary(lm_fx_DEG_f)

#33333
sink(paste(outpath, "fx_DEG_SimpleModels.txt"))
mydata.lm <- lm(fx ~ Genotype*Sex, data = geno_combined_DEG)
anova(mydata.lm)
summary(glht(mydata.lm, emm(pairwise ~ Genotype|Sex, adjust="sidak"))) #consider save to file
summary(glht(mydata.lm, emm(pairwise ~ Sex| Genotype)))
sink()
#3333

#omnibus testing
#https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html#adjust

sink(paste(outpath, "fx_DEG_SimpleStats.txt",sep=''))
'omnibus testing'
joint_tests(ref_grid(lm_fx_DEG)) 
joint_tests(ref_grid(lm_fx_DEG), by = "Sex", adjust = "sidak") 
joint_tests(ref_grid(lm_fx_DEG), by = "Genotype",adjust = "sidak" ) 

'anova'
anova(lm_fx_DEG)
#anova(lm_fx_DEG_f)
#anova(lm_fx_DEG_m)

#post hoc comparison
fx_DEG.emm <- emmeans(lm_fx_DEG , ~ Genotype | Sex, adjust = "sidak")
contrast(fx_DEG.emm, simple = c("Genotype", "Sex")) #FDR
contrast(fx_DEG.emm, simple = list("Genotype", "Sex"))

#post hoc tests
summary(glht(lm_fx_DEG, emm(pairwise ~ Genotype*Sex, contr="sidak"))) #consider save to file
res<-summary(glht(lm_fx_DEG, emm(pairwise ~ Genotype*Sex))) #consider save to file
#summary(as.glht(pairs(lm_fx_DEG.emm), by = NULL))
 
summary(glht(lm_fx_DEG, emm(pairwise ~ Genotype )))
summary(glht(lm_fx_DEG, emm(pairwise ~ Genotype | Sex)))
summary(glht(lm_fx_DEG, emm(pairwise ~ Sex | Genotype)))

mypairs<-pairs(fx_DEG.emm) #_consider save to file
pairs(fx_DEG.emm, by="Genotype")
pairs(fx_DEG.emm, by="Sex")



print('fx DEG')
emmip(lm_fx_DEG, ~ Genotype)
emmip(lm_fx_DEG, ~ Genotype | Sex )
emmip(lm_fx_DEG, ~ Sex | Genotype )
emmip(lm_fx_DEG, Genotype~ Sex  )
sink()

plot(fx_DEG.emm, by = NULL, comparisons = TRUE, adjust = "mvt",
horizontal = FALSE, colors = "darkgreen", main ="fx DEG")
ggsave(paste(outpath,'fx_DEG_emmeans.pdf',sep=''), plot = last_plot(), device='pdf', scale=1, width=16, height=4, unit=c("in"), dpi=200)

```

```{r fx_CLUS_stats, echo='FALSE'}
'simple stats'

print('fx') 

lm_fx_CLUS <- lm(fx ~ Genotype*Sex, geno_combined_CLUS)
summary(lm_fx_CLUS)
lm_fx_CLUS_f <- lm(fx ~ Genotype, combo_f_FA)
#summary(lm_fx_CLUS_f)
lm_fx_CLUS_m <- lm(fx ~ Genotype, combo_m_FA)
#summary(lm_fx_CLUS_f)

#33333
sink(paste(outpath, "fx_CLUS_SimpleModels.txt"))
mydata.lm <- lm(fx ~ Genotype*Sex, data = geno_combined_CLUS)
anova(mydata.lm)
summary(glht(mydata.lm, emm(pairwise ~ Genotype|Sex, adjust="sidak"))) #consider save to file
summary(glht(mydata.lm, emm(pairwise ~ Sex| Genotype)))
sink()
#3333

#omnibus testing
#https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html#adjust

sink(paste(outpath, "fx_CLUS_SimpleStats.txt",sep=''))
'omnibus testing'
joint_tests(ref_grid(lm_fx_CLUS)) 
joint_tests(ref_grid(lm_fx_CLUS), by = "Sex", adjust = "sidak") 
joint_tests(ref_grid(lm_fx_CLUS), by = "Genotype",adjust = "sidak" ) 

'anova'
anova(lm_fx_CLUS)
#anova(lm_fx_CLUS_f)
#anova(lm_fx_CLUS_m)

#post hoc comparison
fx_CLUS.emm <- emmeans(lm_fx_CLUS , ~ Genotype | Sex, adjust = "sidak")
contrast(fx_CLUS.emm, simple = c("Genotype", "Sex")) #FDR
contrast(fx_CLUS.emm, simple = list("Genotype", "Sex"))

#post hoc tests
summary(glht(lm_fx_CLUS, emm(pairwise ~ Genotype*Sex, contr="sidak"))) #consider save to file
res<-summary(glht(lm_fx_CLUS, emm(pairwise ~ Genotype*Sex))) #consider save to file
#summary(as.glht(pairs(lm_fx_CLUS.emm), by = NULL))
summary(glht(lm_fx_CLUS, emm(pairwise ~ Genotype )))
summary(glht(lm_fx_CLUS, emm(pairwise ~ Genotype | Sex)))
summary(glht(lm_fx_CLUS, emm(pairwise ~ Sex | Genotype)))

mypairs<-pairs(fx_CLUS.emm) #_consider save to file
pairs(fx_CLUS.emm, by="Genotype")
pairs(fx_CLUS.emm, by="Sex")



print('fx CLUS') 
emmip(lm_fx_CLUS, ~ Genotype)
emmip(lm_fx_CLUS, ~ Genotype | Sex )
emmip(lm_fx_CLUS, ~ Sex | Genotype )
emmip(lm_fx_CLUS, Genotype~ Sex  )

sink()

plot(fx_CLUS.emm, by = NULL, comparisons = TRUE, adjust = "mvt",
horizontal = FALSE, colors = "darkgreen", main ="fx CLUS")
ggsave(paste(outpath,'fx_CLUS_emmeans.pdf',sep=''), plot = last_plot(), device='pdf', scale=1, width=16, height=4, unit=c("in"), dpi=200)

```
