---
title: "SimpleViolins"
author: "Alex Badea"
date: "10/29/2021"
output: pdf_document
toc: true
---

---
# Data sources

We evaluate genotype and sex differences in mouse models of Alzheimer's disease risk, based on APOE alleles: APOE2 is protective, APOE3 is control, and APOE4 represents genetic risk for AD. One allele increases risk by 3 times, and two APOE4 alleles increase risk by 10 times (ref) in relation to APOE3 . We use multiple data sources:

Morris Water Maze - testing spatial navigation memory
Segmentation: regional volumes
Microstructural properties: FA
Tractography Based Connectivity: Degree, and Clustering Coefficient

We read the data and normalize volumes to the whole brain.

```{r setup, include=FALSE, echo=FALSE,warning = FALSE}


knitr::opts_chunk$set(echo=FALSE,warning = FALSE)
library(tidyverse)
library(export)
library(gridExtra)
library(scales)
library(ggplot2)
library(cowplot)
library(gplots)
library(tidyverse)
library(patternplot)
library(lme4)
library(visreg)
library(tidyr)
library(magrittr) 
library(dplyr)
library(ggpubr)
library(lme4)
library(lsmeans)
library(emmeans)
library(multcomp)
library(zoo)
#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, echo = FALSE)

data <- read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_FA.csv")

data_FA <- read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_FA.csv")

data_VOL <- read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_VOL.csv")

data_DEG<-read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_DEG.csv")

data_CLUS<-read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_CLUS.csv")

outpath='/Users/alex/AlexBadea_MyPapers/DavidDunson/Figures/'

#?data_FA$APOE<-as.factor(data_FA$APOE)?

data_FA <- data_FA %>% 
   filter(Genotype != "HN") 
data_FA$APOE=data_FA$Genotype

data_VOL <- data_VOL %>% 
   filter(Genotype != "HN") 

data_VOL[,15:347]=data_VOL[,15:347]/data_VOL[,348]
data_VOL$APOE=data_VOL$Genotype

data_DEG <- data_DEG %>% 
   filter(Genotype != "HN") 
data_DEG$APOE=data_DEG$Genotype

data_CLUS <- data_CLUS %>% 
   filter(Genotype != "HN") 
data_CLUS$APOE=data_CLUS$Genotype


# separating by sex
geno_combined_FA <- data_FA
combo_f_FA <- geno_combined_FA %>% 
  filter(Sex == "female")
combo_m_FA <- geno_combined_FA %>% 
  filter(Sex == "male")

geno_combined_VOL <- data_VOL
combo_f_VOL <- geno_combined_VOL %>% 
  filter(Sex == "female")
combo_m_VOL <- geno_combined_VOL %>% 
  filter(Sex == "male")

geno_combined_DEG <- data_DEG
combo_f_DEG <- geno_combined_DEG %>% 
  filter(Sex == "female")
combo_m_DEG <- geno_combined_DEG %>% 
  filter(Sex == "male")

geno_combined_CLUS <- data_CLUS
combo_f_CLUS <- geno_combined_CLUS %>% 
  filter(Sex == "female")
combo_m_CLUS <- geno_combined_CLUS %>% 
  filter(Sex == "male")

dodge <- position_dodge(width = 1)
```


# Plots for Winding Number

We embed plots for day d8 probe trials:

```{r winding number plots, echo=FALSE, warning=FALSE}
plot1FA<-ggplot(data_FA, aes(Sex, Probe_d8, fill = Sex)) +
  geom_violin(inherit.aes=TRUE,position=dodge, alpha=0.8) +
  facet_grid(. ~ Genotype)  +
  geom_boxplot(color="black", outlier.color="black", width=0.2, alpha=.8, position=dodge) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=2, alpha=0.6, position=dodge)+
  #geom_jitter(size = 0.1, height = 0, width = 0.1, aes(color = Sex)) + 
  labs(title = "WN: Probe Day d8")+
  theme_minimal()+
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw()+
  labs(x = "genotype", y = "WN: Probe day d8", title = "Winding Number Probe Day d8 ") +
  stat_summary(fun.y=median, geom="point", size=2, color="black") +
  theme_bw() 
 

# plot2FA<-ggplot(data_FA, aes(Sex, Probe_d8, fill = Sex)) +
#   geom_violin(inherit.aes=TRUE,position=dodge, alpha=0.8) +
#   facet_grid(. ~ Genotype)  +
#   geom_boxplot(color="black", outlier.color="black", width=0.2, alpha=.8, position=dodge) +
#   geom_dotplot(binaxis='y', stackdir='center', dotsize=2, alpha=0.6, position=dodge)+
#   #geom_jitter(size = 0.1, height = 0, width = 0.1, aes(color = Sex)) + 
#   labs(title = "WN: Probe Day d8")+
#   theme_minimal()+
#   background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
#   panel_border() + 
#   theme_bw()+
#   labs(x = "genotype", y = "WN: Probe day d8", title = "Winding Number Probe Day d8 ") +
#   stat_summary(fun.y=median, geom="point", size=2, color="black") +
#   theme_bw() 
 
ggdraw() + 
  draw_plot(plot1FA)
# draw_plot(plot1FA, 0, .8, 1, .8) 
#  draw_plot(plot2FA, 0, 0, 1, .8) 

print('Probe day d8') 

lm_Probe_d8 <- lm(Probe_d8 ~ Genotype*Sex, geno_combined_FA)
#summary(lm_Probe_d8)
lm_Probe_d8_f <- lm(Probe_d8 ~ Genotype, combo_f_FA)
#summary(lm_Probe_d8_f)
lm_Probe_d8_m <- lm(Probe_d8 ~ Genotype, combo_m_FA)
#summary(lm_Probe_d8_m)

#33333
sink(paste(outpath, "WindingProbeDay8Models.txt"))
mydata.lm <- lm(Probe_d8 ~ Genotype*Sex, data = geno_combined_FA)
anova(mydata.lm)
summary(glht(mydata.lm, emm(pairwise ~ Genotype|Sex, adjust="sidak"))) #consider save to file
summary(glht(mydata.lm, emm(pairwise ~ Sex| Genotype)))
sink()
#3333

#omnibus testing
#https://cran.r-project.org/web/packages/emmeans/vignettes/confidence-intervals.html#adjust

sink(paste(outpath, "Winding_Probed8_stats102921.txt",sep=''))
'probe day d8'
'omnibus testing'

joint_tests(ref_grid(lm_Probe_d8)) 
joint_tests(ref_grid(lm_Probe_d8), by = "Sex", adjust = "sidak") 
joint_tests(ref_grid(lm_Probe_d8), by = "Genotype",adjust = "sidak" ) 

'anova'
anova(lm_Probe_d8)
#anova(lm_Probe_d8_f)
#anova(lm_Probe_d8_m)

#post hoc comparison
Probe_d8.emm <- emmeans(lm_Probe_d8 , ~ Genotype | Sex, adjust = "sidak")
contrast(Probe_d8.emm, simple = c("Genotype", "Sex")) #FDR
contrast(Probe_d8.emm, simple = list("Genotype", "Sex"))

print('Probe Day d8 Abs Winding Number')
emmip(lm_Probe_d8, ~ Genotype | Sex )

# tw.emm <- contrast(Probe_d8.emm, interaction = c(Genotype = "poly", Sex = "consec"),
# by = NULL)
# tw.emm # see the estimates
# coef(tw.emm) # see the contrast coefficients


#post hoc tests
summary(glht(lm_Probe_d8, emm(pairwise ~ Genotype*Sex, contr="sidak"))) #consider save to file
res<-summary(glht(lm_Probe_d8, emm(pairwise ~ Genotype*Sex))) #consider save to file
#summary(as.glht(pairs(Probe_d8.emm), by = NULL))
 

summary(glht(lm_Probe_d8, emm(pairwise ~ Genotype | Sex)))
summary(glht(lm_Probe_d8, emm(pairwise ~ Sex | Genotype)))

#warpbreaks$tw <- with(warpbreaks, interaction(tension, wool))
#cell <- lm(breaks ~ tw - 1, data = warpbreaks)
#summary(glht(cell, linfct = K))


#emmeans(lm_Probe_d8, ~ Genotype*Sex, contr="tukey")
mypairs<-pairs(Probe_d8.emm) #_consider save to file
pairs(Probe_d8.emm, by="Genotype")
pairs(Probe_d8.emm, by="Sex")
sink()


plot(Probe_d8.emm, by = NULL, comparisons = TRUE, adjust = "mvt",
horizontal = FALSE, colors = "darkgreen", main ="Probe Day d8")
```