---
title: "winding_by_fa"
author: "alexandra badea"
date: "10/4/2021"
output: pdf_document
toc: true
---

# Aim

We examine whether APOE2, APOE3, and APOE4 carriers use a hippocampal or caudate based spatial navigation strategy. 

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
library(cowplot)
library(scales)
# installing packages 
library(tidyverse)
library(cowplot)
library(gplots)
library(ggplot2)
library(patternplot)
library(lme4)
library(visreg)
library(tidyr)
library(magrittr) 
library(dplyr)
library(ggpubr)
library(lme4)
library(lsmeans)
library(emmeans)
library(multcomp)
library(zoo)
#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, echo = FALSE, message=FALSE)
outpath<-'/Users/alex/AlexBadea_MyPapers/DavidDunson/Figures/'

data <- read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_FA.csv")

data_FA <- read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_FA.csv")

data_VOL <- read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_VOL.csv")

data_DEG<-read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_DEG.csv")

data_CLUS<-read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_CLUS.csv")

data <- data %>% 
   filter(Genotype != "HN") 

data_FA <- data_FA %>% 
   filter(Genotype != "HN") 

data_VOL <- data_VOL %>% 
   filter(Genotype != "HN") 

data_VOL[,15:347]=data_VOL[,15:347]/data_VOL[,348]

data_DEG <- data_DEG %>% 
   filter(Genotype != "HN") 

data_CLUS <- data_CLUS %>% 
   filter(Genotype != "HN") 



# separating by sex
geno_combined_FA <- data_FA
combo_f_FA <- geno_combined_FA %>% 
  filter(Sex == "female")
combo_m_FA <- geno_combined_FA %>% 
  filter(Sex == "male")

geno_combined<-geno_combined_FA #temporary fix
combo_f<-combo_f_FA
combo_m<-combo_m_FA

geno_combined_VOL <- data_VOL
combo_f_VOL <- geno_combined_VOL %>% 
  filter(Sex == "female")
combo_m_VOL <- geno_combined_VOL %>% 
  filter(Sex == "male")

geno_combined_DEG <- data_DEG
combo_f_DEG <- geno_combined_DEG %>% 
  filter(Sex == "female")
combo_m_DEG <- geno_combined_DEG %>% 
  filter(Sex == "male")

geno_combined_CLUS <- data_CLUS
combo_f_CLUS <- geno_combined_CLUS %>% 
  filter(Sex == "female")
combo_m_CLUS <- geno_combined_CLUS %>% 
  filter(Sex == "male")

#data[,15:347]=data[,15:347]/data[,348]
  
# ad <- data %>% 
#   filter(! is.na(Weight)) %>% 
#   mutate(sex = case_when(
#     sex == "F" ~ "Female",
#     sex == "M" ~ "Male"
#   )) %>% 
#   filter(risk_for_ad != 3)
# 
# # data by genotypes
# e23 <- ad %>% 
#   filter(genotype == "APOE23") 
# e33 <- ad %>% 
#   filter(genotype == "APOE33")
# e34 <- ad %>% 
#   filter(genotype == "APOE34")
# 
# # combining genotypes 
# geno_combined <- ad %>% 
#   mutate(Genotype = case_when(
#     genotype == "APOE23" | genotype == "APOE33" ~ "APOE3",
#     genotype == "APOE34" | genotype == "APOE44" ~ "APOE4"
#   )) 

#<!-- model<-emmeans(lm, "Sex", adjust = "Tukey") -->
#<!-- pairs(model) -->
#<!-- summary(lm) -->
#<!-- confint(lm) -->


#model<-emmeans(CPu.lm, "Sex", adjust = "Tukey")
#pairs(model)
#summary(lm)
#confint(lm)

```
 

# FA

# Day 5 Probe By Hc FA

``` {r HcFAybDay5Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_FA, aes(x = Hc, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "Hc FA", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_FA, aes(Hc, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  #scale_color_colors(palette = c('blueviolet', 'chartreuse1', 'red'))+
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "Hc FA", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

#------
# #https://stackoverflow.com/questions/65554255/error-while-plotting-with-ggsave-and-other-save-functions
# animal_plots <- foreach(current_animal = c("Dog", "Cats", "Turtle")) %do% {
#     plot_likert(
#       t(graph_data %>% filter(animal == current_animal)),
#       title = "Female",
#       legend.labels = c("strongly disagree","disagree", "neither nor", "agree", "strongly agree"),
#       grid.range = c(1.6, 1.1),
#       expand.grid = FALSE,
#       axis.labels = c(" "),
#       values = "sum.outside",
#       show.prc.sign = TRUE,
#       catcount = 4,
#       cat.neutral = 3
#     )
#   }
#   
#   theplot <- ggarrange(plot1, animal_plots[[1]],
#                        animal_plots[[2]], animal_plots[[3]], 
#                        labels = NULL,
#                        common.legend = TRUE,
#                        legend = "bottom",
#                        ncol = 1, nrow = 4)
#   
#   ggsave(filename=paste(q_column_name, ".png",sep=""), plot=theplot, device = "png")
#   #-----



ggsave(paste(outpath,'Probe5ByHcFA.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")
  


lm <- lm(Probe_d5 ~ Hc*Genotype*Sex, geno_combined_FA)
summary(lm)
lm_f <- lm(Probe_d5 ~ Hc*Genotype, combo_f_FA)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ Hc*Genotype, combo_m_FA)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```

# Day 5 Probe By CPu FA

``` {r CPu:FA Day 5 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_FA, aes(x = CPu, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "CPu FA", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_FA, aes(CPu, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "CPu FA", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5ByCPuFA.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")
lm <- lm(Probe_d5 ~ CPu*Genotype*Sex, geno_combined_FA)
summary(lm)
lm_f <- lm(Probe_d5 ~ CPu*Genotype, combo_f_FA)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ CPu*Genotype, combo_m_FA)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```



# Day 5 Probe By fi FA

``` {r fi:FA Day 5 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_FA, aes(x = fi, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "fi FA", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_FA, aes(fi, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "fi FA", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 
ggsave(paste(outpath,'Probe5ByfiFA.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d5 ~ fi*Genotype*Sex, geno_combined_FA)
summary(lm)
lm_f <- lm(Probe_d5 ~ fi*Genotype, combo_f_FA)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ fi*Genotype, combo_m_FA)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```

# Day 5 Probe By ic FA

``` {r ic_FA_by_ Day5Probe}

plot1 <- ggplot(geno_combined_FA, aes(x = ic, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_FA, aes(ic, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5ByicFA.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d5 ~ ic*Genotype*Sex, geno_combined_FA)
summary(lm)
lm_f <- lm(Probe_d5 ~ ic*Genotype, combo_f_FA)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ ic*Genotype, combo_m_FA)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```

# Day 5 Probe By cbw FA

``` {r icbw_FA_by_Day5Probe}

plot1 <- ggplot(geno_combined_FA, aes(x = cbw, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_FA, aes(cbw, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probed5_cbwFA.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d5 ~ cbw*Genotype*Sex, geno_combined_FA)
summary(lm)
lm_f <- lm(Probe_d5 ~ cbw*Genotype, combo_f_FA)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ cbw*Genotype, combo_m_FA)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```




 



# Day 8 Probe By Hc FA

``` {r HcFAybDay8Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_FA, aes(x = Hc, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 8,  linear model",
       subtitle = "Both males and females",
       x = "Hc FA", y = "WN: Probe Day 8") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_FA, aes(Hc, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 8,  linear model",
       x = "Hc FA", y = "WN: Probe Day 8") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe8ByHcFA.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d8 ~ Hc*Genotype*Sex, geno_combined_FA)
summary(lm)
lm_f <- lm(Probe_d8 ~ Hc*Genotype, combo_f_FA)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ Hc*Genotype, combo_m_FA)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```


# Day 8 Probe By CPu FA


``` {r CPu:FA Day 8 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_FA, aes(x = CPu, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 8,  linear model",
       subtitle = "Both males and females",
       x = "CPu FA", y = "WN: Probe Day 8") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_FA, aes(CPu, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 8,  linear model",
       x = "CPu FA", y = "WN: Probe Day 8") +
  theme(legend.position="none")



ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe8ByCPuFA.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d8 ~ CPu*Genotype*Sex, geno_combined_FA)
summary(lm)
lm_f <- lm(Probe_d8 ~ CPu*Genotype, combo_f_FA)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ CPu*Genotype, combo_m_FA)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```



# Day 8 Probe By fi FA

``` {r fi:FA Day 8 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_FA, aes(x = fi, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 8,  linear model",
       subtitle = "Both males and females",
       x = "fi FA", y = "WN: Probe Day 8") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_FA, aes(fi, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 8,  linear model",
       x = "fi FA", y = "WN: Probe Day 8") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe8ByfiFA.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ fi*Genotype*Sex, geno_combined_FA)
summary(lm)
lm_f <- lm(Probe_d8 ~ fi*Genotype, combo_f_FA)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ fi*Genotype, combo_m_FA)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```

# Day 8 Probe By ic FA

``` {r ic_FA_by_ Day8Probe}

plot1 <- ggplot(geno_combined_FA, aes(x = ic, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_FA, aes(ic, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 


ggsave(paste(outpath,'Probe8ByicFA.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ ic*Genotype*Sex, geno_combined_FA)
summary(lm)
lm_f <- lm(Probe_d8 ~ ic*Genotype, combo_f_FA)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ ic*Genotype, combo_m_FA)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```

# Day 8 Probe By cbw FA


``` {r icbw_FA_by_Day8Probe}

plot1 <- ggplot(geno_combined_FA, aes(x = cbw, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_FA, aes(cbw, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe8BycbwFA.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d8 ~ cbw*Genotype*Sex, geno_combined_FA)
summary(lm)
lm_f <- lm(Probe_d8 ~ cbw*Genotype, combo_f_FA)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ cbw*Genotype, combo_m_FA)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```







# Degree of Connectivity

# Day 5 Probe By Hc DEG

``` {r HcDEGybDay5Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_DEG, aes(x = Hc, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "Hc DEG", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_DEG, aes(Hc, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "Hc DEG", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5ByHcDAEG.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d5 ~ Hc*Genotype*Sex, geno_combined_DEG)
summary(lm)
lm_f <- lm(Probe_d5 ~ Hc*Genotype, combo_f_DEG)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ Hc*Genotype, combo_m_DEG)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```

# Day 5 Probe By CPu DEG

``` {r CPu:DEG Day 5 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_DEG, aes(x = CPu, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "CPu DEG", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_DEG, aes(CPu, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "CPu DEG", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5ByCPuDEG.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d5 ~ CPu*Genotype*Sex, geno_combined_DEG)
summary(lm)
lm_f <- lm(Probe_d5 ~ CPu*Genotype, combo_f_DEG)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ CPu*Genotype, combo_m_DEG)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```



# Day 5 Probe By fi DEG

``` {r fi:DEG Day 5 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_DEG, aes(x = fi, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "fi DEG", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_DEG, aes(fi, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "fi DEG", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 


ggsave(paste(outpath,'Probe5ByfiDEG.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d5 ~ fi*Genotype*Sex, geno_combined_DEG)
summary(lm)
lm_f <- lm(Probe_d5 ~ fi*Genotype, combo_f_DEG)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ fi*Genotype, combo_m_DEG)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```

# Day 5 Probe By ic DEG

``` {r ic_DEG_by_ Day5Probe}

plot1 <- ggplot(geno_combined_DEG, aes(x = ic, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_DEG, aes(ic, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 


ggsave(paste(outpath,'Probe5ByicDEG.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d5 ~ ic*Genotype*Sex, geno_combined_DEG)
summary(lm)
lm_f <- lm(Probe_d5 ~ ic*Genotype, combo_f_DEG)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ ic*Genotype, combo_m_DEG)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```
# Day 5 Probe By cbw DEG

``` {r cbw_DEGbyDay5Probe}
plot1 <- ggplot(geno_combined_DEG, aes(x = cbw, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_DEG, aes(cbw, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5BycbwDEG.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d5 ~ cbw*Genotype*Sex, geno_combined_DEG)
summary(lm)
lm_f <- lm(Probe_d5 ~ cbw*Genotype, combo_f_DEG)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ cbw*Genotype, combo_m_DEG)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```

# Day 8 Probe By Hc DEG

``` {r HcDEGybDay8Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_DEG, aes(x = Hc, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 8,  linear model",
       subtitle = "Both males and females",
       x = "Hc DEG", y = "WN: Probe Day 8") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_DEG, aes(Hc, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 8,  linear model",
       x = "Hc DEG", y = "WN: Probe Day 8") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe8ByHCDEG.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ Hc*Genotype*Sex, geno_combined_DEG)
summary(lm)
lm_f <- lm(Probe_d8 ~ Hc*Genotype, combo_f_DEG)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ Hc*Genotype, combo_m_DEG)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```

# Day 8 Probe By CPu DEG

``` {r CPu:DEG Day8 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_DEG, aes(x = CPu, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 8,  linear model",
       subtitle = "Both males and females",
       x = "CPu DEG", y = "WN: Probe Day 8") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_DEG, aes(CPu, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 8,  linear model",
       x = "CPu DEG", y = "WN: Probe Day 8") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe8ByCPuDEG.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d8 ~ CPu*Genotype*Sex, geno_combined_DEG)
summary(lm)
lm_f <- lm(Probe_d8 ~ CPu*Genotype, combo_f_DEG)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ CPu*Genotype, combo_m_DEG)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```


# Day 8 Probe By fi DEG

``` {r fi:DEG Day 8 Probe}

plot1 <- ggplot(geno_combined_DEG, aes(x = fi, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_DEG, aes(fi, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe8ByfiDEG.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ fi*Genotype*Sex, geno_combined_DEG)
summary(lm)
lm_f <- lm(Probe_d8 ~ fi*Genotype, combo_f_DEG)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ fi*Genotype, combo_m_DEG)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```

# Day 8 Probe By ic DEG

``` {r ic :DEG Day 8 Probe}

plot1 <- ggplot(geno_combined_DEG, aes(x = ic, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_DEG, aes(ic, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe8ByicDEG.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ ic*Genotype*Sex, geno_combined_DEG)
summary(lm)
lm_f <- lm(Probe_d8 ~ ic*Genotype, combo_f_DEG)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ ic*Genotype, combo_m_DEG)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```
# Day 8 Probe By cbw DEG

``` {r cbw_DEG_Day8Probe}
plot1 <- ggplot(geno_combined_DEG, aes(x = cbw, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_DEG, aes(cbw, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5BycbwDEG.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d8 ~ cbw*Genotype*Sex, geno_combined_DEG)
summary(lm)
lm_f <- lm(Probe_d8 ~ cbw*Genotype, combo_f_DEG)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ cbw*Genotype, combo_m_DEG)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```




# Clustering Coefficient

# Day 5 Probe By Hc CLUS

``` {r HcCLUSybDay5Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_CLUS, aes(x = Hc, y = Probe_d5,
                                       color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "Hc CLUS", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_CLUS, aes(Hc, Probe_d5, 
                                       color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "Hc CLUS", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5ByHc_CLUS.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d5 ~ Hc*Genotype*Sex, geno_combined_CLUS)
summary(lm)
lm_f <- lm(Probe_d5 ~ Hc*Genotype, combo_f_CLUS)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ Hc*Genotype, combo_m_CLUS)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```

# Day 5 Probe By CPu CLUS

``` {r CPu:CLUS Day 5 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_CLUS, aes(x = CPu, y = Probe_d5,
                                       color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "CPu CLUS", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_CLUS, aes(CPu, Probe_d5, 
                                       color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "CPu CLUS", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5ByCPu_CLUS.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d5 ~ CPu*Genotype*Sex, geno_combined_CLUS)
summary(lm)
lm_f <- lm(Probe_d5 ~ CPu*Genotype, combo_f_CLUS)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ CPu*Genotype, combo_m_CLUS)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```



# Day 5 Probe By fi CLUS

``` {r fi:CLUS Day 5 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_CLUS, aes(x = fi, y = Probe_d5,
                                       color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "fi CLUS", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_CLUS, aes(fi, Probe_d5, 
                                       color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "fi CLUS", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5Byfi_CLUS.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d5 ~ fi*Genotype*Sex, geno_combined_CLUS)
summary(lm)
lm_f <- lm(Probe_d5 ~ fi*Genotype, combo_f_CLUS)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ fi*Genotype, combo_m_CLUS)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```

# Day 5 Probe By ic CLUS

``` {r ic_CLUS_by_ Day5Probe}

plot1 <- ggplot(geno_combined_CLUS, aes(x = ic, y = Probe_d5,
                                       color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_CLUS, aes(ic, Probe_d5, 
                                       color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5Byic_CLUS.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d5 ~ ic*Genotype*Sex, geno_combined_CLUS)
summary(lm)
lm_f <- lm(Probe_d5 ~ ic*Genotype, combo_f_CLUS)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ ic*Genotype, combo_m_CLUS)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```
# Day 5 Probe By cbw CLUS

``` {r cbw_CLUSbyDay5Probe}
plot1 <- ggplot(geno_combined_CLUS, aes(x = cbw, y = Probe_d5,
                                       color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_CLUS, aes(cbw, Probe_d5, 
                                       color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 


ggsave(paste(outpath,'Probe5Bycbw_CLUS.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d5 ~ cbw*Genotype*Sex, geno_combined_CLUS)
summary(lm)
lm_f <- lm(Probe_d5 ~ cbw*Genotype, combo_f_CLUS)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ cbw*Genotype, combo_m_CLUS)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```

# Day 8 Probe By Hc CLUS

``` {r HcCLUSybDay8Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_CLUS, aes(x = Hc, y = Probe_d8,
                                       color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "Hc CLUS", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_CLUS, aes(Hc, Probe_d8, 
                                       color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "Hc CLUS", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probed8_Hc_CLUS.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ Hc*Genotype*Sex, geno_combined_CLUS)
summary(lm)
lm_f <- lm(Probe_d8 ~ Hc*Genotype, combo_f_CLUS)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ Hc*Genotype, combo_m_CLUS)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```

# Day 8 Probe By CPu CLUS

``` {r CPu:CLUS Day8 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_CLUS, aes(x = CPu, y = Probe_d8,
                                       color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "CPu CLUS", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_CLUS, aes(CPu, Probe_d8, 
                                       color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "CPu CLUS", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probed8_CPu_CLUS.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d8 ~ CPu*Genotype*Sex, geno_combined_CLUS)
summary(lm)
lm_f <- lm(Probe_d8 ~ CPu*Genotype, combo_f_CLUS)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ CPu*Genotype, combo_m_CLUS)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```


# Day 8 Probe By fi CLUS

``` {r fi:CLUS Day 8 Probe}

plot1 <- ggplot(geno_combined_CLUS, aes(x = fi, y = Probe_d8,
                                       color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_CLUS, aes(fi, Probe_d8, 
                                       color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probed8_fi_CLUS.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ fi*Genotype*Sex, geno_combined_CLUS)
summary(lm)
lm_f <- lm(Probe_d8 ~ fi*Genotype, combo_f_CLUS)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ fi*Genotype, combo_m_CLUS)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```

# Day 8 Probe By ic CLUS

``` {r ic :CLUS Day 8 Probe}

plot1 <- ggplot(geno_combined_CLUS, aes(x = ic, y = Probe_d8,
                                       color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_CLUS, aes(ic, Probe_d8, 
                                       color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probed8_ic_CLUS.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ ic*Genotype*Sex, geno_combined_CLUS)
summary(lm)
lm_f <- lm(Probe_d8 ~ ic*Genotype, combo_f_CLUS)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ ic*Genotype, combo_m_CLUS)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```
# Day 8 Probe By cbw CLUS

``` {r cbw_CLUS_Day8Probe}
plot1 <- ggplot(geno_combined_CLUS, aes(x = cbw, y = Probe_d8,
                                       color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_CLUS, aes(cbw, Probe_d8, 
                                       color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probed8_cbw_CLUS.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ cbw*Genotype*Sex, geno_combined_CLUS)
summary(lm)
lm_f <- lm(Probe_d8 ~ cbw*Genotype, combo_f_CLUS)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ cbw*Genotype, combo_m_CLUS)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```







# Volume

# Day 5 Probe By Hc VOL

``` {r HcVOLybDay5Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_VOL, aes(x = Hc, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "Hc VOL", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_VOL, aes(Hc, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "Hc VOL", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5ByHc_VOL.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d5 ~ Hc*Genotype*Sex, geno_combined_VOL)
summary(lm)
lm_f <- lm(Probe_d5 ~ Hc*Genotype, combo_f_VOL)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ Hc*Genotype, combo_m_VOL)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```

# Day 5 Probe By CPu VOL

``` {r CPu:VOL Day 5 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_VOL, aes(x = CPu, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "CPu VOL", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_VOL, aes(CPu, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "CPu VOL", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5ByCPu_VOL.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d5 ~ CPu*Genotype*Sex, geno_combined_VOL)
summary(lm)
lm_f <- lm(Probe_d5 ~ CPu*Genotype, combo_f_VOL)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ CPu*Genotype, combo_m_VOL)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```



# Day 5 Probe By fi VOL

``` {r fi:VOL Day 5 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_VOL, aes(x = fi, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "fi VOL", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_VOL, aes(fi, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "fi VOL", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5Byfi_VOL.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d5 ~ fi*Genotype*Sex, geno_combined_VOL)
summary(lm)
lm_f <- lm(Probe_d5 ~ fi*Genotype, combo_f_VOL)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ fi*Genotype, combo_m_VOL)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```

# Day 5 Probe By ic VOL

``` {r ic_VOL_by_ Day5Probe}

plot1 <- ggplot(geno_combined_VOL, aes(x = ic, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_VOL, aes(ic, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe5Byic_VOL.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")

lm <- lm(Probe_d5 ~ ic*Genotype*Sex, geno_combined_VOL)
summary(lm)
lm_f <- lm(Probe_d5 ~ ic*Genotype, combo_f_VOL)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ ic*Genotype, combo_m_VOL)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```
# Day 5 Probe By cbw VOL

``` {r cbw_VOLbyDay5Probe}
plot1 <- ggplot(geno_combined_VOL, aes(x = cbw, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_VOL, aes(cbw, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

lm <- lm(Probe_d5 ~ cbw*Genotype*Sex, geno_combined_VOL)
summary(lm)
lm_f <- lm(Probe_d5 ~ cbw*Genotype, combo_f_VOL)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ cbw*Genotype, combo_m_VOL)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```

# Day 8 Probe By Hc VOL

``` {r HcVOLybDay8Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_VOL, aes(x = Hc, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "Hc VOL", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_VOL, aes(Hc, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "Hc VOL", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 


ggsave(paste(outpath,'Probe85ByHC_VOL.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ Hc*Genotype*Sex, geno_combined_VOL)
summary(lm)
lm_f <- lm(Probe_d8 ~ Hc*Genotype, combo_f_VOL)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ Hc*Genotype, combo_m_VOL)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```

# Day 8 Probe By CPu VOL

``` {r CPu:VOL Day8 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined_VOL, aes(x = CPu, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "CPu VOL", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot2 <- ggplot(geno_combined_VOL, aes(CPu, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       x = "CPu VOL", y = "WN: Probe Day 5") +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe85ByHC_VOL.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ CPu*Genotype*Sex, geno_combined_VOL)
summary(lm)
lm_f <- lm(Probe_d8 ~ CPu*Genotype, combo_f_VOL)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ CPu*Genotype, combo_m_VOL)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```


# Day 8 Probe By fi VOL

``` {r fi:VOL Day 8 Probe}

plot1 <- ggplot(geno_combined_VOL, aes(x = fi, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_VOL, aes(fi, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe85Byfi_VOL.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ fi*Genotype*Sex, geno_combined_VOL)
summary(lm)
lm_f <- lm(Probe_d8 ~ fi*Genotype, combo_f_VOL)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ fi*Genotype, combo_m_VOL)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```

# Day 8 Probe By ic VOL

``` {r ic :VOL Day 8 Probe}

plot1 <- ggplot(geno_combined_VOL, aes(x = ic, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_VOL, aes(ic, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe85Byic_VOL.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ ic*Genotype*Sex, geno_combined_VOL)
summary(lm)
lm_f <- lm(Probe_d8 ~ ic*Genotype, combo_f_VOL)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ ic*Genotype, combo_m_VOL)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```
# Day 8 Probe By cbw VOL

``` {r cbw_VOL_Day8Probe}
plot1 <- ggplot(geno_combined_VOL, aes(x = cbw, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined_VOL, aes(cbw, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

ggsave(paste(outpath,'Probe85Bycbw_VOL.pdf',sep=''), plot = last_plot(), width=5,height=5,units=c("in"), dpi=200, device = "pdf")


lm <- lm(Probe_d8 ~ cbw*Genotype*Sex, geno_combined_VOL)
summary(lm)
lm_f <- lm(Probe_d8 ~ cbw*Genotype, combo_f_VOL)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ cbw*Genotype, combo_m_VOL)
summary(lm_m)

#males and females
anova(lm)
#females
anova(lm_f)
#males
anova(lm_m)

```