---
title: "winding_by_fa"
author: "alexandra badea"
date: "10/4/2021"
output: pdf_document
toc: true
---

#Aim 1

We examine whether APOE2, APOE3, and APOE4 carriers use a hippocampal or caudate based spatial navigation strategy. 

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
library(cowplot)
library(scales)
# installing packages 
library(tidyverse)
library(cowplot)
library(gplots)
library(ggplot2)
library(patternplot)
library(lme4)
library(visreg)
library(tidyr)
library(magrittr) 
library(dplyr)
library(ggpubr)
library(lme4)
library(lsmeans)
library(emmeans)
library(multcomp)
library(zoo)
#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, echo = FALSE, message=FALSE)


data <- read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_FA.csv")

data_FA <- read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_FA.csv")

data_VOL <- read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_VOL.csv")

data_DEG<-read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_DEG.csv")

data_CLUS<-read.csv("/Users/alex/AlexBadea_MyPapers/DavidDunson/dropbox/WindingNumber/APOE22APOE33APOE44Young_CLUS.csv")

data <- data %>% 
   filter(Genotype != "HN") 

data_FA <- data_FA %>% 
   filter(Genotype != "HN") 

data_VOL <- data_VOL %>% 
   filter(Genotype != "HN") 

data_VOL[,15:347]=data_VOL[,15:347]/data_VOL[,348]

data_DEG <- data_DEG %>% 
   filter(Genotype != "HN") 

data_CLUS <- data_CLUS %>% 
   filter(Genotype != "HN") 



# separating by sex
geno_combined_FA <- data_FA
combo_f_FA <- geno_combined_FA %>% 
  filter(Sex == "female")
combo_m_FA <- geno_combined_FA %>% 
  filter(Sex == "male")

geno_combined_VOL <- data_VOL
combo_f_VOL <- geno_combined_VOL %>% 
  filter(Sex == "female")
combo_m_VOL <- geno_combined_VOL %>% 
  filter(Sex == "male")

geno_combined_DEG <- data_DEG
combo_f_DEG <- geno_combined_DEG %>% 
  filter(Sex == "female")
combo_m_DEG <- geno_combined_DEG %>% 
  filter(Sex == "male")

geno_combined_CLUS <- data_CLUS
combo_f_CLUS <- geno_combined_CLUS %>% 
  filter(Sex == "female")
combo_m_CLUS <- geno_combined_CLUS %>% 
  filter(Sex == "male")

#data[,15:347]=data[,15:347]/data[,348]
  
# ad <- data %>% 
#   filter(! is.na(Weight)) %>% 
#   mutate(sex = case_when(
#     sex == "F" ~ "Female",
#     sex == "M" ~ "Male"
#   )) %>% 
#   filter(risk_for_ad != 3)
# 
# # data by genotypes
# e23 <- ad %>% 
#   filter(genotype == "APOE23") 
# e33 <- ad %>% 
#   filter(genotype == "APOE33")
# e34 <- ad %>% 
#   filter(genotype == "APOE34")
# 
# # combining genotypes 
# geno_combined <- ad %>% 
#   mutate(Genotype = case_when(
#     genotype == "APOE23" | genotype == "APOE33" ~ "APOE3",
#     genotype == "APOE34" | genotype == "APOE44" ~ "APOE4"
#   )) 




```
 

```{r violin winding numbers, echo = FALSE, message=FALSE, quiet = TRUE }
# separating by sex
geno_combined <- data
combo_f <- geno_combined %>% 
  filter(Sex == "female")
combo_m <- geno_combined %>% 
  filter(Sex == "male")

p<-ggplot(data, aes(Genotype, Probe_d5, fill = Sex)) +
  geom_violin(alpha = 0.5) +
  facet_grid(. ~ Genotype)  +
  #geom_boxplot(width = 0.1, outlier.color = "red") +
  geom_jitter(size = 0.01, height = 0, width = 0.1, aes(color = Sex)) + 
  geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1))+
  labs(title = "Probe Trial: Day 5")+
  theme_minimal()+
geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1))+
  stat_summary(fun.y=median, geom="point", size=2, color="black")+
 theme_bw() 
 
 
plot1<-ggplot(data, aes(Genotype, Probe_d5, fill = Sex)) +
  geom_violin(alpha = 0.5) +
  facet_grid(. ~ Genotype)  +
  geom_boxplot(width = 0.1, outlier.color = "red") +
  geom_jitter(size = 0.01, height = 0, width = 0.1, aes(color = Sex)) + 
  geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1))+
  labs(title = "Probe Trial: Day 5")+
  theme_minimal()+
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw()+
  labs(x = "genotype", y = "Probe day 5", title = "") +
geom_dotplot(binaxis='y', stackdir='center', position=position_dodge(1))+
  stat_summary(fun.y=median, geom="point", size=2, color="black")+
 theme_bw() 
 
 plot1<-ggplot(data, aes(Sex, Probe_d5, fill = Sex)) +
  geom_violin(alpha = 0.5) +
  facet_grid(. ~ Genotype)  +
  #geom_boxplot(width = 0.1, outlier.color = "red") +
  geom_jitter(size = 0.01, height = 0, width = 0.1, aes(color = Sex)) + 
  geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1))+
  labs(title = "Probe Trial: Day 5")+
  theme_minimal()+
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw()+
  labs(x = "genotype", y = "Probe day 8", title = "") +
geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1)) +
stat_summary(fun.y=median, geom="point", size=2, color="black") +
 theme_bw() 
 

plot2<-ggplot(data, aes(Sex, Probe_d8, fill = Sex)) +
  geom_violin(alpha = 0.5) +
  facet_grid(. ~ Genotype)  +
  #geom_boxplot(width = 0.1, outlier.color = "red") +
  geom_jitter(size = 0.01, height = 0, width = 0.1, aes(color = Sex)) + 
  geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1))+
  labs(title = "Probe Trial: Day 8")+
  theme_minimal()+
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw()+
  labs(x = "genotype", y = "Probe day 8", title = "") +
geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1)) +
stat_summary(fun.y=median, geom="point", size=2, color="black") +
 theme_bw() 
 


ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 


lm <- lm(Probe_d5 ~ Genotype*Sex, geno_combined)

summary(lm)

# emmip(lm, type ~ Genotype | Animal)
# colors <- c("red", "green", "blue")
# plot3 <-plot (emmeans(lm, ~ Genotype | Sex) , 
#                 col=colors(data$Genotype), main="Probe Day5")
# draw(plot3)
# 
# plot3 <-plot (emmeans(lm, ~ Genotype * Sex) ,  main="Probe Day5")
# 
# legend("bottomright", legend = paste("Probe Day5", 1:3), col = Genotype, pch = 19, bty = "n")
# 
#  ggdraw(plot3)

 ###alex pairs
 probed5.lm <- lm(Probe_d5 ~ Genotype*Sex, data = data)
warp.emm <- emmeans(probed5.lm , ~ Genotype | Sex)
contrast(warp.emm, "poly") # inherits 'by = "wool"' from warp.emm
pairs(warp.emm) # ditto
contrast(warp.emm, "eff", by = NULL) # contrasts of the 6 factor combs
pairs(warp.emm, simple = "Sex") # same as pairs(warp.emm, by = "tension")
# Do all "simple" comparisons, combined into one family
pairs(warp.emm, simple = "each", combine = TRUE)
 
contrast(warp.emm, simple = list("Genotype", "Sex"))

contrast(warp.emm, simple = c("Genotype", "Sex"))

tw.emm <- contrast(warp.emm, interaction = c(Genotype = "poly", Sex = "consec"),
by = NULL)
tw.emm # see the estimates
coef(tw.emm) # see the contrast coefficients

# warp.lm <- lm(breaks ~ wool*tension, data = warpbreaks)
# warp.emm <- emmeans(warp.lm, ~ tension | wool)
# contrast(warp.emm, "poly") # inherits 'by = "wool"' from warp.emm
# pairs(warp.emm) # ditto
# contrast(warp.emm, "eff", by = NULL) # contrasts of the 6 factor combs
# pairs(warp.emm, simple = "wool") # same as pairs(warp.emm, by = "tension")
# # Do all "simple" comparisons, combined into one family
# pairs(warp.emm, simple = "each", combine = TRUE)
#  ###alex pairs

####
warp.lm <- lm(Probe_d5 ~ Genotype*Sex, data = data)
warp.emm <- emmeans(warp.lm, ~ Genotype | Sex)
contrast(warp.emm, "poly")

pairs(warp.emm)

### Setting up a custom contrast function
helmert.emmc <- function(levs, ...) {
M <- as.data.frame(contr.helmert(levs))
names(M) <- paste(levs[-1],"vs earlier")
attr(M, "desc") <- "Helmert contrasts"
M
}
contrast(warp.emm, "helmert")
## Not run:
# See what is used for polynomial contrasts with 6 levels
emmeans:::poly.emmc(1:6)
## End(Not run)

###
####
Probe5.lm <- lm(Probe_d5 ~ Genotype * Sex, data = data)
emm <- emmeans(Probe5.lm, "Genotype")
eff_size(emm, sigma = sigma(Probe5.lm), edf = df.residual(Probe5.lm))
# or equivalently:
eff_size(pairs(emm), sigma(Probe5.lm), df.residual(Probe5.lm), method = "identity")
# ### Mixed model example:
# if (require(nlme)) {
# Oats.lme <- lme(yield ~ Variety + factor(nitro),
# random = ~ 1 | Block / Variety,
# data = Oats)
# # Combine variance estimates
# VarCorr(Oats.lme)
# totSD <- sqrt(214.4724 + 109.6931 + 162.5590)
# # I figure edf is somewhere between 5 (Blocks df) and 51 (Resid df)
# emmV <- emmeans(Oats.lme, ~ Variety)
# print(eff_size(emmV, sigma = totSD, edf = 5))
# print(eff_size(emmV, sigma = totSD, edf = 51))
# }
# Multivariate model for the same data:
# MOats.lm <- lm(yield ~ Variety, data = MOats)
# eff_size(emmeans(MOats.lm, "Variety"),
# sigma = sqrt(mean(sigma(MOats.lm)^2)), # RMS of sigma()
# edf = df.residual(MOats.lm))
# These results illustrate a sobering message that effect sizes are often
# not nearly as accurate as you may think.


summary(glht(Probe5.lm, emm(pairwise ~ Genotype | Sex)))

####

lm_f <- lm(Probe_d5 ~ Genotype, combo_f)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ Genotype, combo_m)
summary(lm_m)

anova(lm)
anova(lm_f)
anova(lm_m)



model<-emmeans(lm, "Sex", adjust = "Tukey")
pairs(model)
summary(lm)
confint(lm)

model<-emmeans(lm, "Genotype", adjust = "Tukey")
pairs(model)
summary(lm)
confint(lm)


lm <- lm(Probe_d8 ~ Genotype*Sex, geno_combined)
summary(lm)
lm_f <- lm(Probe_d8 ~ Genotype, combo_f)
summary(lm_f)
lm_m <- lm(Probe_d8 ~ Genotype, combo_m)
summary(lm_m)

anova(lm)
anova(lm_f)
anova(lm_m)
```




```
{r volume, echo = FALSE, message=FALSE, quiet = TRUE }

# separating by sex
geno_combined <- data_VOL
combo_f <- geno_combined %>% 
  filter(Sex == "female")
combo_m <- geno_combined %>% 
  filter(Sex == "male")

p<-ggplot(data_VOL, aes(Genotype, Hc, fill = Sex)) +
  geom_violin(alpha = 0.5) +
  facet_grid(. ~ Genotype)  +
  #geom_boxplot(width = 0.1, outlier.color = "red") +
  geom_jitter(size = 0.01, height = 0, width = 0.1, aes(color = Sex)) + 
  geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1))+
  labs(title = "Hc Volume")+
  theme_minimal()+
geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1))+
  stat_summary(fun.y=median, geom="point", size=2, color="black")+
 theme_bw() 
 
 
#
#  
 plot1<-ggplot(data_VOL, aes(Sex, Hc, fill = Sex)) +
  geom_violin(alpha = 0.5) +
  facet_grid(. ~ Genotype)  +
  #geom_boxplot(width = 0.1, outlier.color = "red") +
  geom_jitter(size = 0.01, height = 0, width = 0.1, aes(color = Sex)) + 
  geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1))+
  labs(title = "Hc Volume (%)")+
  theme_minimal()+
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw()+
  labs(x = "genotype", y = "Hc Volume (%)", title = "") +
geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1)) +
stat_summary(fun.y=median, geom="point", size=2, color="black") +
 theme_bw() 
 

plot2<-ggplot(data_VOL, aes(Sex, CPu, fill = Sex)) +
  geom_violin(alpha = 0.5) +
  facet_grid(. ~ Genotype)  +
  #geom_boxplot(width = 0.1, outlier.color = "red") +
  geom_jitter(size = 0.01, height = 0, width = 0.1, aes(color = Sex)) + 
  geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1))+
  labs(title = "CPu Volume (%)")+
  theme_minimal()+
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw()+
  labs(x = "genotype", y = "CPu Volume (%)", title = "") +
geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1)) +
stat_summary(fun.y=median, geom="point", size=2, color="black") +
 theme_bw() 
 


ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 


lm <- lm(Hc ~ Genotype*Sex, geno_combined)

summary(lm)

# emmip(lm, type ~ Genotype | Animal)
# colors <- c("red", "green", "blue")
# plot3 <-plot (emmeans(lm, ~ Genotype | Sex) , 
#                 col=colors(data$Genotype), main="Probe Day5")
# draw(plot3)
# 
# plot3 <-plot (emmeans(lm, ~ Genotype * Sex) ,  main="Probe Day5")
# 
# legend("bottomright", legend = paste("Probe Day5", 1:3), col = Genotype, pch = 19, bty = "n")
# 
#  ggdraw(plot3)

 ###alex pairs
 Hc.lm <- lm(Hc ~ Genotype*Sex, data = data)
warp.emm <- emmeans(Hc.lm , ~ Genotype | Sex)
contrast(warp.emm, "poly") # inherits 'by = "wool"' from warp.emm
pairs(warp.emm) # ditto
contrast(warp.emm, "eff", by = NULL) # contrasts of the 6 factor combs
pairs(warp.emm, simple = "Sex") # same as pairs(warp.emm, by = "tension")
# Do all "simple" comparisons, combined into one family
pairs(warp.emm, simple = "each", combine = TRUE)
 
contrast(warp.emm, simple = list("Genotype", "Sex"))

contrast(warp.emm, simple = c("Genotype", "Sex"))

tw.emm <- contrast(warp.emm, interaction = c(Genotype = "poly", Sex = "consec"),
by = NULL)
tw.emm # see the estimates
coef(tw.emm) # see the contrast coefficients

# warp.lm <- lm(breaks ~ wool*tension, data = warpbreaks)
# warp.emm <- emmeans(warp.lm, ~ tension | wool)
# contrast(warp.emm, "poly") # inherits 'by = "wool"' from warp.emm
# pairs(warp.emm) # ditto
# contrast(warp.emm, "eff", by = NULL) # contrasts of the 6 factor combs
# pairs(warp.emm, simple = "wool") # same as pairs(warp.emm, by = "tension")
# # Do all "simple" comparisons, combined into one family
# pairs(warp.emm, simple = "each", combine = TRUE)
#  ###alex pairs

####
warp.lm <- lm(Hc ~ Genotype*Sex, data = data)
warp.emm <- emmeans(warp.lm, ~ Genotype | Sex)
contrast(warp.emm, "poly")

pairs(warp.emm)

### Setting up a custom contrast function
helmert.emmc <- function(levs, ...) {
M <- as.data.frame(contr.helmert(levs))
names(M) <- paste(levs[-1],"vs earlier")
attr(M, "desc") <- "Helmert contrasts"
M
}
contrast(warp.emm, "helmert")
## Not run:
# See what is used for polynomial contrasts with 6 levels
emmeans:::poly.emmc(1:6)
## End(Not run)

###
####
Hc.lm <- lm(Hc ~ Genotype * Sex, data = data)
emm <- emmeans(Hc.lm, "Genotype")
eff_size(emm, sigma = sigma(Hc.lm), edf = df.residual(Hc.lm))
# or equivalently:
eff_size(pairs(emm), sigma(Hc.lm), df.residual(Hc.lm), method = "identity")
# ### Mixed model example:
# if (require(nlme)) {
# Oats.lme <- lme(yield ~ Variety + factor(nitro),
# random = ~ 1 | Block / Variety,
# data = Oats)
# # Combine variance estimates
# VarCorr(Oats.lme)
# totSD <- sqrt(214.4724 + 109.6931 + 162.5590)
# # I figure edf is somewhere between 5 (Blocks df) and 51 (Resid df)
# emmV <- emmeans(Oats.lme, ~ Variety)
# print(eff_size(emmV, sigma = totSD, edf = 5))
# print(eff_size(emmV, sigma = totSD, edf = 51))
# }
# Multivariate model for the same data:
# MOats.lm <- lm(yield ~ Variety, data = MOats)
# eff_size(emmeans(MOats.lm, "Variety"),
# sigma = sqrt(mean(sigma(MOats.lm)^2)), # RMS of sigma()
# edf = df.residual(MOats.lm))
# These results illustrate a sobering message that effect sizes are often
# not nearly as accurate as you may think.


summary(glht(Hc.lm, emm(pairwise ~ Genotype | Sex)))

####

lm_f <- lm(Hc ~ Genotype, combo_f)
summary(lm_f)
lm_m <- lm(Hc ~ Genotype, combo_m)
summary(lm_m)

anova(lm)
anova(lm_f)
anova(lm_m)



model<-emmeans(Hc.lm, "Sex", adjust = "Tukey")
pairs(model)
summary(lm)
confint(lm)

model<-emmeans(Hc.lm, "Genotype", adjust = "Tukey")
pairs(model)
summary(lm)
confint(lm)


lm.CPu <- lm(CPu ~ Genotype*Sex, geno_combined)
summary(lm)
lm_f <- lm(CPu ~ Genotype, combo_f)
summary(lm_f)
lm_m <- lm(CPu ~ Genotype, combo_m)
summary(lm_m)

anova(lm.CPu)
anova(lm_f)
anova(lm_m)
``````


```
{r violin FA, echo = FALSE}
#volumes, FAs, DEG , CLUS plots
# separating by sex
geno_combined <- data_FA
combo_f <- geno_combined %>% 
  filter(Sex == "female")
combo_m <- geno_combined %>% 
  filter(Sex == "male")


 plot1<-ggplot(data_FA, aes(Sex, fi, fill = Sex)) +
  geom_violin(alpha = 0.5) 
  facet_grid(. ~ Genotype)  +
  #geom_boxplot(width = 0.1, outlier.color = "red") +
  geom_jitter(size = 0.01, height = 0, width = 0.1, aes(color = Sex)) + 
  geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1))+
  labs(title = "fi:FA")+
  theme_minimal()+
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw()+
  labs(x = "genotype", y = "fi", title = "") +
geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1)) +
stat_summary(fun.y=median, geom="point", size=2, color="black") +
 theme_bw() 
 

plot2<-ggplot(data_FA, aes(Sex, ic, fill = Sex)) +
  geom_violin(alpha = 0.5) +
  facet_grid(. ~ Genotype)  +
  #geom_boxplot(width = 0.1, outlier.color = "red") +
  geom_jitter(size = 0.01, height = 0, width = 0.1, aes(color = Sex)) + 
  geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1))+
  labs(title = "ic:FA")+
  theme_minimal()+
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw()+
  labs(x = "genotype", y = "fi", title = "") +
geom_dotplot(binaxis='y', stackdir='center',
                 position=position_dodge(1)) +
stat_summary(fun.y=median, geom="point", size=2, color="black") +
 theme_bw() 
 


ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot2, 0, 0, 1, .5) 


#end volume, FAs, DEG, CLUST plots
```



``` {r fi:FA Day 5 Probe, echo = FALSE}

plot1 <- ggplot(geno_combined, aes(x = fi, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() +
  labs(title = "Winding Number: Probe Day 5,  linear model",
       subtitle = "Both males and females",
       x = "Age", y = "WN: Probe Day 5") +
  theme_bw() +
  background_grid(major = "xy", minor = "none") 

plot4 <- ggplot(geno_combined, aes(fi, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

lm <- lm(Probe_d5 ~ Genotype*Sex, geno_combined)
summary(lm)
lm_f <- lm(Probe_d5 ~ Genotype, combo_f)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ Genotype, combo_m)
summary(lm_m)

anova(lm)
anova(lm_f)
anova(lm_m)


#lm1<-lm(NormSWDist ~ Sex + factor(APOE), probe_trials)
#model<-emmeans(lm1, "Sex", adjust = "Tukey")
#pairs(model)

```


``` {r ic:FA Day 5 Probe}

plot1 <- ggplot(geno_combined, aes(x = ic, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined, aes(ic, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

lm <- lm(Probe_d5 ~ Genotype*Sex, geno_combined)
summary(lm)
lm_f <- lm(Probe_d5 ~ Genotype, combo_f)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ Genotype, combo_m)
summary(lm_m)

anova(lm)
anova(lm_f)
anova(lm_m)

```

``` {r cbw FA Day 5 Probe}
plot1 <- ggplot(geno_combined, aes(x = cbw, y = Probe_d5,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined, aes(cbw, Probe_d5, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

lm <- lm(Probe_d5 ~ Genotype*Sex, geno_combined)
summary(lm)
lm_f <- lm(Probe_d5 ~ Genotype, combo_f)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ Genotype, combo_m)
summary(lm_m)

anova(lm)
anova(lm_f)
anova(lm_m)

```


``` {r fi:FA Day 8 Probe}

plot1 <- ggplot(geno_combined, aes(x = fi, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined, aes(fi, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

lm <- lm(Probe_d5 ~ Genotype*Sex, geno_combined)
summary(lm)
lm_f <- lm(Probe_d5 ~ Genotype, combo_f)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ Genotype, combo_m)
summary(lm_m)

anova(lm)
anova(lm_f)
anova(lm_m)

```


``` {r ic :FA Day 8 Probe}

plot1 <- ggplot(geno_combined, aes(x = ic, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined, aes(ic, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

lm <- lm(Probe_d5 ~ Genotype*Sex, geno_combined)
summary(lm)
lm_f <- lm(Probe_d5 ~ Genotype, combo_f)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ Genotype, combo_m)
summary(lm_m)

anova(lm)
anova(lm_f)
anova(lm_m)

```

``` {r cbw:FA Day 8 Probe}
plot1 <- ggplot(geno_combined, aes(x = cbw, y = Probe_d8,
                          color = Genotype,  fill = Genotype)) + 
  geom_point(aes(shape = Sex)) +
  geom_smooth(formula = y ~ x, method = "lm") +
  theme_bw() 

plot4 <- ggplot(geno_combined, aes(cbw, Probe_d8, 
                                   color = Genotype, fill = Genotype)) + 
  geom_point(aes(shape = Genotype)) + 
  facet_grid(. ~ Sex) + 
  stat_smooth(method = "lm") +
  background_grid(major = 'xy', minor = "none") + # add thin horizontal lines 
  panel_border() + 
  theme_bw() +
  theme(legend.position="none")

ggdraw() + 
  draw_plot(plot1, 0, .5, 1, .5) +
  draw_plot(plot4, 0, 0, 1, .5) 

lm <- lm(Probe_d5 ~ Genotype*Sex, geno_combined)
summary(lm)
lm_f <- lm(Probe_d5 ~ Genotype, combo_f)
summary(lm_f)
lm_m <- lm(Probe_d5 ~ Genotype, combo_m)
summary(lm_m)

anova(lm)
anova(lm_f)
anova(lm_m)

```